Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
Minor changes
updated label of all figures
added comment related to CPU time and timeout

\item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability). 
\end{enumerate}

@@

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.

\textcolor{red}{we have to describe the timeout...}

>>>>

\item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
\item Division is only needed for positive numbers in this implementation (where it is needed for checking stability). 
\end{enumerate}

@@

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.

\textcolor{red}{Pascal, Can you please describe our we measure time?
All times given are wall clock time in seconds as measured by the UNIX date command.}

\textcolor{red}{Pascal, can you please describe the timeout?}
